Verifying Demonstrations

### 2019-07-02 paper/distance-bounding.tex
Puts labels on definitions (distance-bounding)

\begin{definition}[Tainted session, \acs*{DBMF}~\cite{DB-DFKO}]
  A time-critical round
  \(\Xscript{\sid}{k, k+1} = (m_k, \dotsc, m_{k+1})\)
  of an adversary--verifier session~\(\sid\), where \(m_k\) is sent by the 
  verifier, is \emph{tainted} by the round
  \(\Xscript{\sid'}{k', k'+1} = (m_{k'}, m_{k'+1})\)
  of a prover--adversary session~\(\sid'\) if
  \begin{align*}
    (m_k, m_{k+1}) &= (m_{k'}, m_{k'+1}) \\
    \marker[\sid, k] &< \marker[\sid', k'] \\
    \marker[\sid, k+1] &> \marker[\sid', k'+1].
  \end{align*}
\end{definition}

@@

\begin{definition}[\acs*{DBMF} resistance~\cite{TREAD}]
  For \iac{DB} authentication scheme \(\DB\), a \((t, \qobs, \qp, \qv)\)-MF 
  adversary \(\adv\) \emph{wins} against \(\DB\) if the verifier accepts 
  \(\adv\) in in one of the \(\qv\) adversary--verifier sessions \(\sid\), 
  which does not have any critical phase tainted by a prover--adversary session 
  \(\sid'\).
  The protocol \(\DB\) is \Ac{DBMF} resistant if the probability 
  \(\Adv_{\DB}^{\text{MF}}(\adv)\) that \(\adv\) wins the game is negligible in 
  the security parameter.
\end{definition}

@@

\begin{definition}[Tainted session, \acs*{DBTF}]
  A time-critical round
  \(\Xscript{\sid}{k, k+1} = (m_k, m_{k+1})\)
  of an adversary--verifier session~\(\sid\), where \(m_k\) is sent by the 
  verifier, is \emph{tainted} by the round
  \(\Xscript{\sid'}{k', k'+1} = (m_{k'}, m_{k'+1})\)
  of a prover--adversary session~\(\sid'\) if
  \begin{align*}
    \marker[\sid, k] &< \marker[\sid', k'] \\
    \marker[\sid, k'+1] &> \marker[\sid', k'+1].
  \end{align*}
\end{definition}

\begin{definition}[strSimTF resistance~\cite{FormalTerroristFraud}]
  \dots
\end{definition}

@@

\begin{definition}[Tainted session, \acs*{DBDH}~\cite{TREAD}]
  \dots
\end{definition}

\begin{definition}[\acs*{DBDH} resistance~\cite{TREAD}]
  \dots
\end{definition}

>>>>

\begin{definition}[Tainted session, \acs*{DBMF}~\cite{DB-DFKO}]%
  \label{TaintedMF}
  A time-critical round
  \(\Xscript{\sid}{k, k+1} = (m_k, \dotsc, m_{k+1})\)
  of an adversary--verifier session~\(\sid\), where \(m_k\) is sent by the 
  verifier, is \emph{tainted} by the round
  \(\Xscript{\sid'}{k', k'+1} = (m_{k'}, m_{k'+1})\)
  of a prover--adversary session~\(\sid'\) if
  \begin{align*}
    (m_k, m_{k+1}) &= (m_{k'}, m_{k'+1}) \\
    \marker[\sid, k] &< \marker[\sid', k'] \\
    \marker[\sid, k+1] &> \marker[\sid', k'+1].
  \end{align*}
\end{definition}

@@

\begin{definition}[\acs*{DBMF} resistance~\cite{TREAD}]%
  \label{MFresistance}
  For \iac{DB} authentication scheme \(\DB\), a \((t, \qobs, \qp, \qv)\)-MF 
  adversary \(\adv\) \emph{wins} against \(\DB\) if the verifier accepts 
  \(\adv\) in in one of the \(\qv\) adversary--verifier sessions \(\sid\), 
  which does not have any critical phase tainted by a prover--adversary session 
  \(\sid'\).
  The protocol \(\DB\) is \Ac{DBMF} resistant if the probability 
  \(\Adv_{\DB}^{\text{MF}}(\adv)\) that \(\adv\) wins the game is negligible in 
  the security parameter.
\end{definition}

@@

\begin{definition}[Tainted session, \acs*{DBTF}]\label{TaintedTF}
  A time-critical round
  \(\Xscript{\sid}{k, k+1} = (m_k, m_{k+1})\)
  of an adversary--verifier session~\(\sid\), where \(m_k\) is sent by the 
  verifier, is \emph{tainted} by the round
  \(\Xscript{\sid'}{k', k'+1} = (m_{k'}, m_{k'+1})\)
  of a prover--adversary session~\(\sid'\) if
  \begin{align*}
    \marker[\sid, k] &< \marker[\sid', k'] \\
    \marker[\sid, k'+1] &> \marker[\sid', k'+1].
  \end{align*}
\end{definition}

\begin{definition}[strSimTF resistance~\cite{FormalTerroristFraud}]%
  \label{TFresistance}
  \dots
\end{definition}

@@

\begin{definition}[Tainted session, \acs*{DBDH}~\cite{TREAD}]%
  \label{TaintedDH}
  \dots
\end{definition}

\begin{definition}[\acs*{DBDH} resistance~\cite{TREAD}]%
  \label{DHresistance}
  \dots
\end{definition}
